The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-04 paper/main.tex
paper: formatting fix
fix typo
paper: text improvements

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and treatment of detection efficiencies.
Given a somewhat restrictive set of assumptions, we derive a general formula 
for the apparent rate density, for which the free parameters include the true 
planet radius distribution, and also the relative numbers of planets 
orbiting secondaries, primaries, and single stars.
From this formalism, we suggest that for most of the observed radius 
distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
One corollary is that binarity seems unlikely to strongly influence the HJ 
rate discrepancy.
The errors created by ignoring binarity at smaller apparent radii might be 
larger: for instance, the absolute occurrence of Earth-sized planets could be 
overestimated by up to $\approx 50\%$.
A final point is that our formalism provides a quantitative argument for why
whenever high-resolution imaging follow-up discovers stellar neighbors of 
detected planets, the planet is more likely to orbit the primary. 
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

An immediate complication is that, due to dynamical stability or some 
aspect of planet formation, the occurrence rate of planets might differ 
between binary and single-star systems.
In an observed sample of stars that contains both singles and binaries, the 
detected planets would then be drawn from different intrinsic 
distributions for the occurrence rates in single star systems, 
about primaries, and about secondaries~\citep[{\it 
e.g},][]{wang_occurrence_2015}.

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
searchable point on the sky might be two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:discussion} for discussion of this 
issue).

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of searchable stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of stars that are searchable for a given observed transit depth is greater 
than that the multiplicity fraction in a volume limited sample.
This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
are searchable out to larger distances than single stars because they are more 
luminous.
While this is what biases detectability, separate effects bias interpretation:
ignoring binarity, the (apparent) radii assigned to planets in binaries will 
typically be smaller than the true radii.
The apparent and true radii differ because of diluting flux, and possibly 
because the planet is assumed to orbit the wrong 
star.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys.
First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
which all planets have identical properties, and all stars have identical 
properties except that some are in binary systems.
The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
generalized in Sec.~\ref{sec:general_formula} to allow for varying populations 
of secondaries, and for varying intrinsic occurrence rate distributions.
Sec.~\ref{sec:more_complicated} investigates questions of interest, 
including (a) measurements of $\eta_\oplus$, (b) the ``hot Jupiter rate 
discrepancy'', and (c) \citet{fulton_california-_2017}'s 
recently discovered ``valley''.
We discuss what our models suggest about binarity's biasing effects in 
Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, assume a stellar mass $M\a=M_1$, and estimate both a stellar 
radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

To assess the severity of these errors, we need to assume a binary fraction, 
and to know the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,$ and $Z_2$).
For the former,
\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$, 
which we take as a binary fraction. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$. 
For the latter, we take $Z_0=Z_1=Z_2=0.5$, and plot the resulting occurrence 
rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.

Our point for comparison is the rate density for single stars,
\begin{equation}
\Gamma_0(r) = Z_0 \cdot \delta(r-r\p).
\end{equation}
We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
of the apparent to single star rate density,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r}.
\end{equation}
Continuing in the assumption that the number of planets per single, primary, 
and secondary star are equal, we find a rate density 
correction factor at the true planet radius of $1/(1+\mu)$.
This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
    BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate at $r\a=r\p$ would be 
half the true rate at $r=r\p$.
For most stellar types, the twin binary fraction is not that high.

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes $(1+2\mu)/(1+\mu)^2$.
This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
While it seems unlikely that secondaries are planet-less, 
it is worth noting that $\Gamma\a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.

@@

A simple extension to the previous example will help us further distinguish 
the detected populations.
Consider now a universe that is the same in every respect to that of 
Sec.~\ref{sec:model_1}, except that half of planets have radii $r\p$, while 
the other half have $r\p/\sqrt{2}$.
The true rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an SNR 
limited transit survey in which the true masses of all the singles and 
primaries are known by the observer.
We let the properties of the secondaries vary, and assume that there are some 
functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
terms of its mass.
We then allow for a volume-limited mass ratio distribution $f(q)$, which is 
assumed to be independent of the primary's mass.
We also allow arbitrary true rate densities for singles, primaries, 
and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
Since the properties of the secondaries vary, we must consider not only the 
dependence of the rate densities on planet radius, but also on stellar mass.
We presume that the observers always take the properties of a binary system to 
be those of the primary.

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
($\mathcal{B}$) is the dilution term for primaries (secondaries).
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Eq.~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this reduces to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which may be written in a closed form using the hypergeometric function.

@@

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability it having a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

\section{More complicated transit survey models}
\label{sec:more_complicated}
The following section applies our general equation for the apparent rate 
density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in more 
realistic regimes.
In general, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
This section will consider the effects of varying both $f_i(r)$ and also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
radius distribution of planets vary.
Specifically, we take
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is quite similar to that of the twin 
binary, fixed-planet case (Eq.~\ref{eq:model_1_apparent_rate_density}), except 
that the radius dependence and normalization are slightly different:
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right].
\label{eq:model5_apparent_rate_density}
\end{equation}
As in Sec.~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles then becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Note though that it could change if the $Z_i$'s are not equal.
Also, a power law radius distribution $f(r) \propto r^\delta$ diverges for 
$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
approximation is good for $r\a\gtrsim 2r_\oplus$.
Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
hot Jupiters.
An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
We are not particularly interested in this effect; there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Sec.~\ref{sec:further_models}.
If the assumptions behind this model (listed in 
Sec.~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
binarity's impact on derived occurrence rates is quite small.

@@

It would be nice to get some intuition for how much the secondaries matter.
From Fig.~\ref{fig:model_1_volumes}, we have the intuition that for a given 
true planet radius, secondaries have a much smaller searchable volume than 
primaries or singles.
Does this necessarily imply that if we are given a detected planet with some 
apparent radius $r\a$, which is then observed by high-resolution imaging to 
exist in a binary, that the planet probably orbits the primary?

>>>>

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
We pay particular attention to dilution of observed planet radii, errors in 
star counts, and treatment of detection efficiencies.
Given a plausible set of assumptions, we derive a general formula 
for the apparent rate density, which depends on the true 
planet radius distribution, and also the relative numbers of planets 
orbiting secondaries, primaries, and single stars.
From this formalism, we suggest that for most of the observed radius 
distribution (apparent planet radii $>2r_\oplus$), ignoring binarity 
leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
One corollary is that binarity seems unlikely to strongly influence any 
discrepancy between transit survey and RV survey hot Jupiter rates.
The errors created by ignoring binarity at smaller apparent radii might be 
larger: for instance, the absolute occurrence of Earth-sized planets could be 
overestimated by $\lesssim 50\%$.
Under our formalism, we also show that if high-resolution imaging reveals 
stellar neighbors of detected planets, the planet is usually more likely to 
orbit the primary. We explore how this statement depends on the
apparent radius of the detected planet.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

An immediate complication is that, due to dynamical stability or some 
aspect of planet formation, the occurrence rate of planets might differ 
between binary and single-star systems.
In an observed sample of stars that contains both singles and binaries, the 
detected planets would then be drawn from different intrinsic 
distributions for the occurrence rates in single star systems, 
about primaries, and about secondaries~\citep[{\it 
e.g.},][]{wang_occurrence_2015}.

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
searchable point on the sky might be two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars.

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of searchable stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of stars that are searchable for a given observed transit depth is greater 
than that the multiplicity fraction in a volume limited sample.
This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
are searchable out to larger distances than single stars because they are more 
luminous.
A separate effect is that the apparent radii assigned to planets in binaries 
will typically be smaller than the true radii.
Correcting for ``radius dilution'' requires knowing both the amount flux 
contributed by each source in a photometric aperture, and which star the 
planet orbits.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys.
First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
which all planets have identical properties, and all stars have identical 
properties except that some are in binary systems.
We generalize these thought-experiments in 
Sec.~\ref{sec:general_formula} to allow for realistic stellar populations with 
arbitrary occurrence rate distributions.
Sec.~\ref{sec:more_complicated} explores the implications for
(a) measurements of $\eta_\oplus$,
(b) the ``hot Jupiter rate discrepancy'', and 
(c) \citet{fulton_california-_2017}'s recently discovered ``valley''.
We discuss what our models suggest about the importance of binarity's biases 
in Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, assume a stellar mass $M\a=M_1$, and estimate a stellar 
radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

To assess the severity of these errors, we need to assume a binary fraction, 
and to know the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,$ and $Z_2$).
For the former,
\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$, 
which we take as a binary fraction. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$. 
For the true number of planets per star, we take $Z_0=Z_1=Z_2=0.5$, and plot 
the resulting occurrence rates as a function of planet radius in 
Fig.~\ref{fig:occ_rate_model_1}.

Our point for comparison is the rate density for single stars,
\begin{equation}
\Gamma_0(r) = Z_0 \cdot \delta(r-r\p).
\end{equation}
We define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
of the apparent to single star rate density,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r}.
\end{equation}
Continuing in the assumption that the number of planets per single, primary, 
and secondary star are equal, then the rate density 
correction factor at the true planet radius is $1/(1+\mu)$.
This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
    BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate at $r\a=r\p$ would be 
half the true rate at $r=r\p$.
For most stellar types, the twin binary fraction is not that high.

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes $(1+2\mu)/(1+\mu)^2$.
This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
While it seems unlikely that secondaries are planet-less, 
the fact that $\Gamma\a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary will become important as we 
proceed.

@@

A simple extension to the previous example will help us further distinguish 
the detected populations.
Consider now a universe that is the same in every respect to that of 
Sec.~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
while the other half have true radii $r\p/\sqrt{2}$.
The true rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an 
SNR-limited transit survey in which the singles and primaries can have 
arbitrary properties, but their true masses are known by the observer.
We assume that there are some functions $L(M)$ and $R(M)$ that specify a 
star's luminosity and radius in terms of its mass, and that the volume-limited 
binary mass ratio distribution, $f(q)$, is independent of the primary's mass.
We also allow arbitrary true rate densities for singles, primaries, 
and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).
We presume that the observers always take the properties of a binary system to 
be those of the primary.

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
($\mathcal{B}$) is the dilution term for primaries (secondaries).
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Eq.~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which may be written in a closed form using the hypergeometric function.

@@

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

\section{More complicated transit survey models}
\label{sec:more_complicated}
The following section applies our general equation for the apparent rate 
density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in regimes 
of observational interest.
In general, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
This section will consider the effects of varying both $f_i(r)$ and also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
radius distribution of planets vary.
Specifically, we take
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is quite similar to that of the twin 
binary, fixed-planet case (Eq.~\ref{eq:model_1_apparent_rate_density}), except 
for a slightly different radius dependence and normalization:
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right].
\label{eq:model5_apparent_rate_density}
\end{equation}
As in Sec.~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Note though that it could change if the $Z_i$'s are not equal.
Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
approximation is good for $r\a\gtrsim 2r_\oplus$.
Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
hot Jupiters.
An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
We are not particularly interested in this effect; there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Sec.~\ref{sec:further_models}.
If the assumptions behind this model (listed in 
Sec.~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
binarity's impact on derived occurrence rates is quite small.

@@

It would be nice to improve our intuition for how much the secondaries matter.
We have the understanding that for a given true planet radius, secondaries 
have a much smaller searchable volume than primaries or singles.
Does this necessarily imply that if we are given a detected planet with some 
apparent radius $r\a$, which is then observed by high-resolution imaging to 
exist in a binary, that the planet probably orbits the primary?
